Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

Our testbed is comprised of several popular cryptography libraries. We choose them based
on the following aspects. First, they should be widely used in many popular software.
In general, it is hard to implement a secure cryptography library from scratch. So most
software only use a few number of well-known cryptography libraries. Second, we choose some
libraries which are well studied in the previous work. We can refer to these conclusions to
verify our results. Based on the two requirements, we evaluate \tool{} on the following libraries:
OpenSSL, Libgcrypt, mbedTLS, Monocypher. OpenSSL, Libgcrypt, and mebdTLS are the most widely used
cryptography libraries. OpenSSL and mbedTLS have been widely studied in the previous research.
Monocyper is designed to be side-channel resistant. We use the library to test if our tool has any
false positives. We also test \tool{} on some simple countermeasure implementations.

@@

Table~\ref{chapter4:table:over_result} shows an overview of the evaluation results. 
\tool{} also finds that most side-channel
vulnerabilities leak very little information, which confirms our
initial assumption.  
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from the severe ones.

Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
\tool{} confirms that these leakage comes from table lookups. The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem. These changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.

>>>>

Our testbed is comprised of several popular cryptography libraries. We choose them based
on the following aspects. First, they should be widely used in many popular software.
In general, it is hard to implement a secure cryptography library from scratch. So most
software only use a few number of well-known cryptography libraries. Second, we choose some
libraries which are well studied in the previous work. We can refer to these conclusions to
verify our results. Based on the two requirements, we evaluate \tool{} on the following libraries:
OpenSSL, Libgcrypt, mbedTLS, and Monocypher. OpenSSL, Libgcrypt, and mebdTLS are the most widely used
cryptography libraries. OpenSSL and mbedTLS have been widely studied in the previous research.
Monocyper is designed to be side-channel resistant. We use the library to test if our tool has any
false positives. We also test \tool{} on some simple countermeasure implementations.

@@

Table~\ref{chapter4:table:over_result} shows an overview of the evaluation results. 
\tool{} also finds that most side-channel
vulnerabilities leak very little information, which confirms our
initial assumption.  
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research~\cite{Bonneau11894063_16,Gullasch:2011:CGB:2006077.2006784} has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from the severe ones.

Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
\tool{} confirms that these leakage come from table lookups. The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem. These changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
